### 2012-02-11 paper.tex
Added a (not 100% complete) figure showing the extreme temperature dependence

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}

@@

The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time. Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure \ref{fgr:full_oscillation}. A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered. At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.

>>>>

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
  \label{fgr:full_oscillation}
\end{figure*}

@@

The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time. Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}. A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered. At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.

A very destinct temperature dependence is seen on the oscillation frequency, an example is given in Figure~\ref{fgr:temperature_dependence}. The exact magnitude is not completely consistent between samples, but the effect is always large. This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step, the oscillation period was apprixmately 500\,s, after the step, the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}
